---
title: "Research Question 2 - space before punctuation"
author: "Frenk C.J. van Mil"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
---

```{r, result='hide', echo=FALSE, include=FALSE}
source('statistics.R')
```

```{r, results='hide', echo=FALSE, include=FALSE}
transformations <- list(
  c(13, log10_transform)
)
dbs_res <- readdbs('selected_dev_parsed', 'selected_dev_parsed_space_punctuation', transformations = transformations, where='liwc_filled_yarkoni=1')

data_og <- dbs_res$db1
data_cmp <- dbs_res$db2

dfs <- list(data_og, data_cmp)
dfnames = c('original', 'space')
rm(dbs_res)
```

```{r}
# Drop the PI columns for now.
data_og <- data_og[c(1,7:16)]
data_cmp <- data_cmp[c(1,7:16)]
dfs <- list(data_og, data_cmp)
```

In order to evaluate research question 2, we need to connect to the MySQL database first. From the database we fetch to dataframes, _data\_og_ (scores with all preprocessing steps enabled) and _data\_cmp_ (scores without at space before punctuation parsing). Any column indicating significance (signf) means a `p-value` below `0.05` is found.

## Summarize data
```{r}
summarize_df(dfs, dfnames=dfnames, fix_naming=TRUE)
```

From the summary of above, we can see that some columns do not seem to be affected (much). For example, PI extraversion and neuroticism are not really affected by the parsing. However, all other columns of all methods seem to be affected at least some. We should check, however, if this is significant or not.

Furthermore, by looking at the median and the mean, we can see that it seems that most column are not too skewed to one side. Therefore, normallity may be possible.

First we check if there even is a difference in a single row and column.

```{r}
inspect_AE_differences(df1 = data_og, df2 = data_cmp)
```

```{r}
latex_table(func=inspect_AE_differences, 
            caption=paste("Differences in scores for PI with and without", dfnames[[2]], "parsing."),
            label=paste0('tab:', dfnames[[2]],'_diff'),
            include_index = TRUE,
            fix_column = 0,
            df1 = data_og, df2 = data_cmp)
```

There are no differences, so no further inspection required.
