---
title: "Research Question 2 - url"
author: "Frenk C.J. van Mil"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
---

```{r, result='hide', echo=FALSE, include=FALSE}
source('statistics.R')
```

```{r, results='hide', echo=FALSE, include=FALSE}
transformations <- list(
  c(13, log10_transform)
)
dbs_res <- readdbs('selected_dev_parsed', 'selected_dev_parsed_images', transformations = transformations)

data_og <- dbs_res$db1
data_cmp <- dbs_res$db2

dfs <- list(data_og, data_cmp)
dfnames = c('original', 'images')
rm(dbs_res)
```

In order to evaluate research question 2, we need to connect to the MySQL database first. From the database we fetch to dataframes, _data\_og_ (scores with all preprocessing steps enabled) and _data\_cmp_ (scores without at image parsing). Any column indicating significance (signf) means a `p-value` below `0.05` is found.

## Summarize data
```{r}
summarize_df(dfs, dfnames=dfnames, fix_naming=TRUE)
```

From the summary of above, we can see that some columns do not seem to be affected (much). For example, PI extraversion and neuroticism are not really affected by the parsing. However, all other columns of all methods seem to be affected at least some. We should check, however, if this is significant or not.

Furthermore, by looking at the median and the mean, we can see that it seems that most column are not too skewed to one side. Therefore, normallity may be possible.

First we check if there even is a difference in a single row and column.

```{r}
inspect_AE_differences(df1 = data_og, df2 = data_cmp)
```

```{r}
latex_table(func=inspect_AE_differences, 
            caption=paste("Absolute differences in scores for PI with and without", dfnames[[2]], "parsing."),
            label=paste0('tab:', dfnames[[2]],'_diff'),
            include_index = TRUE,
            fix_column = 0,
            df1 = data_og, df2 = data_cmp)
```

Then we will look if the distributions are normal or not. To visualize this, we draw histograms, density plots, and QQ-plots.

```{r}
hist_all(data_og, data_cmp)
```

```{r}
density_all(data_og, data_cmp, name2=dfnames[[2]])
```

```{r, cache=TRUE}
draw_qqplots(data_og, data_cmp)
```

By looking at the QQ-plots, we can see that some appear at least near-normally distributed. However, most do not seem to be normally distributed.


## Shapiro-Wilk Normality test
To make check our findings of the QQ-plots, we could use Shapiro-Wilk normality testing to check if the traits are significantly non-normal.
```{r}
sample_size <- 50
repeats <- 1000
shap_og <- shap(data_og, sample_size=sample_size)
print(shap_og)

shap_cmp <- shap(data_cmp, sample_size=sample_size)
print(shap_cmp)

repeated(shap, repeats, data_og, sample_size, p=0.05) # Check if the p-values are most of the time right.
repeated(shap, repeats, data_og, sample_size=sample_size, p=0.05) # Check if the p-values are most of the time right.
```


From the above we can conclude that the data is significanlty different from a normal distribution for the following columns:
- PI:
  - Openness
- Golbeck:
  - Openness
  - Extraversion
  - Neuroticism

```{r}
normal_cols <- c(1,3:11,13:15)
non_normal_cols <- c(1,2,12,16)
```

## Fisher test (compare variances)
Before we can compare whether there is a difference in means, we first need to compare the variances.

```{r}
fisherf_df <- fisherf(data_og, data_cmp)
fisherf_df
```

## Wilcox signed rank test with continuaty correction (paired = TRUE)
```{r}
wilc_df <- wilc(data_og[,non_normal_cols], data_cmp[,non_normal_cols], paired = TRUE)
wilc_df
```

## T-test
```{r}
ttest_df <- ttest(data_og[,normal_cols], data_cmp[,normal_cols])
ttest_df
```

## Effect size mean - Cohen's d
```{r}
cohensd_df <- cohensd(data_og[,normal_cols], data_cmp[,normal_cols])
cohensd_df
```

```{r}
latex_table(func=wilc, caption=paste("Paired Wilcoxon signed-rank test between the original data and", dfnames[[2]],"parsing disabled."), label=paste0("tab:",dfnames[[2]],"_wilcox"), df1=data_og[,non_normal_cols], df2=data_cmp[,non_normal_cols], p=0.05, paired=TRUE)
```

```{r}
latex_table(func=ttest_eff, caption=paste("Paired t-test and Cohen's d effect sizes between the original data and", dfnames[[2]],"parsing disabled."), label=paste0("tab:",dfnames[[2]],"_ttest"), df1=data_og[,normal_cols], df2=data_cmp[,normal_cols], p=0.05, paired=TRUE)
```

## Plots
```{r}
plot_line_ordered(data_og, data_cmp)
```

```{r}
trait_boxplots(data_og, data_cmp)
```

```{r}
ggplot_line_ordered(data_og, data_cmp)
```

```{r}
gt <- get_ground_truth()

insp <- inspect_gt_non_zero(data_og, data_cmp, dfnames=dfnames, gt=gt)
insp
```

```{r}
diff_cols <- get_diff_cols(insp)

latex_table(inspect_gt_non_zero, caption=paste("Difference in RMSE and MAE scores with the original dataset compared to the", dfnames[[2]],"dataset."), label=paste0("tab:",dfnames[[2]],"_gt_RMSE_MAE"), include_index=TRUE, fix_column=0, transpose=TRUE, df1=data_og, df2=data_cmp, dfnames=dfnames, gt=gt, columns=diff_cols)
```
