---
title: "Research Question 3"
author: "Frenk C.J. van Mil"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
---

```{r, result='hide', echo=FALSE, include=FALSE}
source('statistics.R')
knitr::opts_chunk$set(comment = NA)
knitr::opts_chunk$set(results = 'asis')
```

### Read in data
```{r, results='hide', echo=FALSE, include=FALSE}
transformations <- list(
  c(13, log10_transform)
)
dbs_res1 <- readdbs('selected_dev_parsed_rq3_3000', 'selected_dev_parsed_rq3_1200', transformations = transformations)
dbs_res2 <- readdbs('selected_dev_parsed_rq3_600', 'selected_dev_parsed_rq3_100', transformations = transformations)

data_full <- read_single_db('selected_dev_parsed', transformations=transformations)

data_3000 <- dbs_res1$db1
data_1200 <- dbs_res1$db2
data_600 <- dbs_res2$db1
data_100 <- dbs_res2$db2

rm(dbs_res1)
rm(dbs_res2)

data_3000 <- data_3000[(data_3000$id %in% data_100$id),]
data_1200 <- data_1200[(data_1200$id %in% data_100$id),]

dfs <- list(data_100, data_600, data_1200, data_3000)
dfnames=list('[100]','[600]', '[1200]', '[3000>')
```
First we read in the data and save this to four different datasets: data_3000 (comments with >3000 words), data_1200 (comments truncated to 1200 words), data_600 (comments truncated to 6000 words), and data_100 (comments truncated to 100 words).

```{r}
summarize_df(dfs, dfnames=dfnames)
```

### Compare density plots
```{r}
cols <- colnames(data_3000)
for (i in 2:length(cols)) {
  column <- cols[i]
  density3000 <- density(data_3000[,i])
  density1200 <- density(data_1200[,i])
  density600 <- density(data_600[,i])
  density100 <- density(data_100[,i])
  maximum <- max(max(max(density3000[['y']]),max(density1200[['y']])),max(max(density600[['y']]),max(density100[['y']])))
  plot(density3000, main=paste('Density plot',column), col=color$c_sc1, ylim=c(0,maximum))
  lines(density1200, col=color$c_sc2)
  lines(density600, col=color$c_sc3)
  lines(density100, col=color$c_sc4)
  legend(x="topright", y=0.92, legend=dfnames, col=c(color$c_sc1,color$c_sc2,color$c_sc3,color$c_sc4), pch=rep('-',length(dfnames)), lwd=10)
}
```

```{r}
get_ylim <- function(dfs, column) {
  ylim_lower <- 1
  ylim_upper <- 0
  for (df in dfs) {
    lowerq <- quantile(df[,column])[2]
    upperq <- quantile(df[,column])[4]
    iqr <- upperq - lowerq
    ylim_lower <- min(lowerq - (iqr*1.5),ylim_lower)
    ylim_upper <- max((iqr*1.5) + upperq,ylim_upper)
  }
  return(c(ylim_lower,ylim_upper))
}
```

```{r}
outline = FALSE
for (i in 2:length(cols)) {
  column <- cols[i]
  at_pos <- c(0.25,0.75,1.25,1.75)
  
  boxplot(data_100[,i], xlim=c(0,2), ylim=get_ylim(dfs,i), at=at_pos[1], main=paste('Boxplots',column), col=color$c_sc4, outline=outline)
  boxplot(data_600[,i], add=TRUE, at=at_pos[2], col=color$c_sc3, outline=outline)
  boxplot(data_1200[,i], add=TRUE, at=at_pos[3], col=color$c_sc2, outline=outline)
  boxplot(data_3000[,i], add=TRUE, at=at_pos[4], col=color$c_sc1, outline=outline)
  axis(1, 1:length(dfnames), labels=dfnames, at=at_pos)
}
```

```{r}
variances_rq3 <- function() {
  for (column in 2:length(data_3000)) {
    print(paste0(colnames(data_3000)[column], ":"))
    cat(paste("\tVariance [100]:", round(var(data_100[,column]),3),
              "\n\tVariance [600]:", round(var(data_600[,column]),3),
              "\n\tVariance [1200]:", round(var(data_1200[,column]),3),
              "\n\tVariance [3000]:", round(var(data_3000[,column]),3),
              "\n")
        )
  }
}
variances_rq3()
```
```{r}
repeated_shap_rq3 <- function() {
  iterations = 1000
  sample_size = 50
  p = 0.05
  
  print('Data [100]')
  repeated(shap, n=iterations, df=data_100, sample_size=sample_size, p=p)
  print('Data [600]')
  repeated(shap, n=iterations, df=data_600, sample_size=sample_size, p=p)
  print('Data [1200]')
  repeated(shap, n=iterations, df=data_1200, sample_size=sample_size, p=p)
  print('Data [3000]')
  repeated(shap, n=iterations, df=data_3000, sample_size=sample_size, p=p)
}
repeated_shap_rq3()
```
```{r}
normal_cols <- c(1,3:5,7:9,11,13:15)
non_normal_cols <- c(1,2,6,10,12,16)
```


### Normality with QQ-Plots
```{r}
draw_qqplots_rq3 <- function(dfs, dfnames) {
  for (i in 1:length(dfs)) {
    df <- dfs[[i]]
    for (column in 2:length(df)) {
      qqnorm(df[,column], pch=1, frame=FALSE, main = paste0(dfnames[[i]],": ",colnames(df)[[column]]))
      qqline(df[,column], col="steelblue", lwd=2)
    }
  }
}
draw_qqplots_rq3(dfs, dfnames)
```

```{r}
# Textually describe the dataframes.
summarize_df_rq3 <- function(df1, df2, df3, df4, dfnames=c(NULL,NULL,NULL,NULL)) {
  
  summ_df <- data.frame(Df=character(),
                        Column=character(), 
                        Min=double(), 
                        '1st Qu.'=double(), 
                        Median=double(), 
                        Mean=double(), 
                        '3rd Qu.'=double(), 
                        Max=double(), 
                        stringsAsFactors = FALSE)
  
  summarize_col <- function(in_df, i, res_df, dfname) {
    dfname <- ifelse(is.null(dfname), deparse(substitute(in_df)), dfname)
    res <- summary(in_df[,i])
    res_df[nrow(res_df)+1, ] <- c(dfname,
                                  colnames(in_df)[i],
                                  round(res['Min.'],2),
                                  round(res['1st Qu.'],2), 
                                  round(res['Median'],2),
                                  round(res['Mean'],2),
                                  round(res['3rd Qu.'],2),
                                  round(res['Max.'],2))
    res_df
  }
  for (i in 2:length(colnames(df1))) {
    summ_df <- summarize_col(df1, i, summ_df, dfnames[1])
    summ_df <- summarize_col(df2, i, summ_df, dfnames[2])
    summ_df <- summarize_col(df3, i, summ_df, dfnames[3])
    summ_df <- summarize_col(df4, i, summ_df, dfnames[4])
  }
  summ_df
}

## Summarize data
summarize_df_rq3(data_100, data_600, data_1200, data_3000)
```

### Fisher F test to compare two variances.
```{r}
## Compare Fisher-F test for all dataframes.
compare(fisherf, dfs=dfs, dfnames=dfnames, p=0.05)
```

### Wilcox signed-rank test.
```{r}
## Compare Wilc signed-rank test for all dataframes.
compare(wilc, dfs=dfs, dfnames=dfnames, paired=TRUE, p=0.05, columns=non_normal_cols)
```

### T-test.
```{r}
## Compare Wilc signed-rank test for all dataframes.
compare(ttest, dfs=dfs, dfnames=dfnames, paired=TRUE, p=0.05, columns=normal_cols)
```

### Cohen's d.
```{r}
## Compare Wilc signed-rank test for all dataframes.
compare(cohensd, dfs=dfs, dfnames=dfnames, columns=normal_cols)
```

# Ground-truth inspection
```{r}
gt <- get_ground_truth()
traits = c('Openness', 'Conscientiousness', 'Extraversion', 'Agreeableness', 'Neuroticism')
```

```{r}
# Get the squared-error.
SE(data_100, gt)
```
```{r}
# Get the Mean-quared-error.
MSE(data_100, gt)
```

```{r}
# Get the Root-mean-squared-error, which is NRMSE (normalized) at the same time due to 0-1 scaling!
RMSE(data_100, gt)
```

```{r}
# Get the Mean-Absolute-Error.
MAE(data_100, gt)
```


```{r}
# Check the RMSE on each personality trait.
measure_plot(dfs=dfs, dfnames=dfnames, gt=gt, func=RMSE, std=0.95)
```

```{r}
# Check the MAE on each personality trait.
measure_plot(dfs=dfs, dfnames=dfnames, gt=gt, func=MAE)
```

```{r}
# Check the maximum absolute error on each personality trait.
measure_plot(dfs=dfs, dfnames=dfnames, gt=gt, func=max_AE)
```

```{r}
scatter <- function(df, gt, default_scaling=TRUE) {
  for (i in 2:16) {
    trait_idx <- (i - 2) %% 5 + 1
    trait <- traits[[trait_idx]]
    df.m <- merge(df, gt, by="id")
    p <- ggplot() + 
      geom_point(data=df.m, aes(x=df.m[,i], y=df.m[,(trait_idx+16)])) +
      geom_abline(intercept = 0, slope = 1) +
      ggtitle(paste(colnames(df.m)[i], 'vs', colnames(df.m)[trait_idx+16])) +
      xlab(colnames(df.m)[i]) + ylab(colnames(df.m)[trait_idx+16])
    if (default_scaling) {
      p <- p + scale_x_continuous(limits=c(0, 1), breaks=unlist(lapply(c(1:10), FUN=function(x) x/10))) +
        scale_y_continuous(limits=c(0, 1), breaks=unlist(lapply(c(1:10), FUN=function(x) x/10)))
    }
    print(p)
  }
}
scatter(data_100, gt)
```

```{r}
scatter(data_600, gt)
```

```{r}
scatter(data_1200, gt)
```

```{r}
scatter(data_3000, gt)
```

```{r}
centralize <- function(df, columns, rounding=2) {
  df.mean <- data.frame(df[,1:tail(columns,1)])
  df.mean[,columns] <- df.mean[,columns] - colMeans(df.mean[,columns])
  if (rounding > -1) {
    df.mean[,columns] <- round(df.mean[,columns], rounding)
  }
  return(df.mean)
}
scatter(centralize(data_100, columns=c(2:16)), centralize(gt, columns=c(2:6)), default_scaling = FALSE)
```

```{r}
fifty_quantile <- quantile(gt$word_count, .5)[['50%']]
small_gt <- data.frame(gt[gt[,"word_count"] < fifty_quantile,])
large_gt <- gt[gt[,"word_count"] >= fifty_quantile,]

# Check the RMSE on each personality trait.
measure_plot_gts(df=data_full, dfnames=c('<50%','>50%'), gts=list(small_gt,large_gt), func=RMSE)
measure_plot_gts(df=data_full, dfnames=c('<50%','>50%'), gts=list(small_gt,large_gt), func=MAE)
```

Now lets try the same but set the limit to 600.
```{r}
fifty_quantile <- 600
small_gt <- data.frame(gt[gt[,"word_count"] < fifty_quantile,])
large_gt <- gt[gt[,"word_count"] >= fifty_quantile,]

# Check the RMSE on each personality trait.
measure_plot_gts(df=data_full, dfnames=c('<50%','>50%'), gts=list(small_gt,large_gt), func=RMSE)
measure_plot_gts(df=data_full, dfnames=c('<50%','>50%'), gts=list(small_gt,large_gt), func=MAE)
```

```{r}
abs_difference_plot <- function(df1, df2, gt) {
  ae1 <- AE(df1, gt)
  ae2 <- AE(df2, gt)
  for (trait_idx in 1:5) {
    pi_idx <- trait_idx + 1
    yark_idx <- trait_idx + 6
    golb_idx <- trait_idx + 11
    
    plot(1:nrow(ae1), sort(ae1[,pi_idx]), type='n',
         main=paste0('Absolute differences sorted [',traits[[trait_idx]],']'),
         xlab='People',
         ylab='Absolute difference')
    lines(1:nrow(ae1), sort(ae1[,pi_idx]), col=color$c1)
    lines(1:nrow(ae1), sort(ae1[,yark_idx]), col=color$c2)
    lines(1:nrow(ae1), sort(ae1[,golb_idx]), col=color$c3)
    lines(1:nrow(ae2), sort(ae2[,pi_idx]), col=color$c1, lty=2)
    lines(1:nrow(ae2), sort(ae2[,yark_idx]), col=color$c2, lty=2)
    lines(1:nrow(ae2), sort(ae2[,golb_idx]), col=color$c3, lty=2)
    legend(x="topleft", y=0.92, 
           c('PI','Yarkoni','Golbeck', 'df1', 'df2'),
           col=c(color$c1,color$c2,color$c3,'black','black'),
           pch=rep('-',5), lwd=4, lty=c(rep(1,4),3))
  }
}
abs_difference_plot(data_100, data_1200, gt)
```
```{r}
abs_difference_plot(data_100, data_600, gt)
```

```{r}
abs_difference_plot(data_1200, data_3000, gt)
```

```{r}
method_words_plot <- function(dfs, dfnames, gt, method) {
  aes <- list()
  for (df in dfs) {
    aes[[length(aes) + 1]] <- AE(df, gt)
  }

  if (method == "PI") {
    method_idx <- 1
  } else if (method == "Yarkoni") {
    method_idx <- 6
  } else if(method == "Golbeck") {
    method_idx <- 11
  }
  
  for (trait_idx in 1:5) {
    idx <- trait_idx + method_idx
    
    plot(1:nrow(aes[[1]]), sort(aes[[1]][,idx]), type='n',
         main=paste0(method,' - Absolute differences sorted [',traits[[trait_idx]],']'),
         xlab='People',
         ylab='Absolute difference')
    for (df_i in 1:length(dfs)) {
      nrows <- nrow(aes[[df_i]])
      lines(1:nrow(aes[[df_i]]), sort(aes[[df_i]][,idx]), col=color[[df_i]])
    }
    legend(x="topleft", y=0.92, dfnames, col=colors(1:length(dfs)), pch=rep('-',length(dfs)), lwd=4)
  }

}
method_words_plot(dfs, dfnames, gt, method="PI")
```

```{r}
method_words_plot(dfs, dfnames, gt, method="Yarkoni")
```

```{r}
method_words_plot(dfs, dfnames, gt, method="Golbeck")
```

```{r}
difference_plot <- function(df, gt) {
  df <- df[df$id %in% gt$id,]
  gt <- gt[gt$id %in% df$id,]
  
  merged <- merge(df, gt[1:6], by="id")
  for (i in 1:5) {
    pi_idx <- i + 1
    yark_idx <- i + 6
    golb_idx <- i + 11
    gt_idx <- i + 16
    
    ordered_merged <- merged[order(merged[,gt_idx], merged[,pi_idx], merged[,yark_idx], merged[,golb_idx]),]

    plot(1:nrow(ordered_merged), ordered_merged[,gt_idx], type='n',
         main=paste0('Ordered scores [',traits[[i]],']'),
         xlab='People',
         ylab='Absolute difference')
    lines(1:nrow(ordered_merged), ordered_merged[,gt_idx], col='black')
    lines(1:nrow(ordered_merged), ordered_merged[,pi_idx], col=alphcolor('c1',0.8))
    lines(1:nrow(ordered_merged), ordered_merged[,yark_idx], col=alphcolor('c2',0.8))
    lines(1:nrow(ordered_merged), ordered_merged[,golb_idx], col=alphcolor('c3',0.8))
    legend(x="topleft", y=0.92, c('gt','pi','yarkoni','golbeck'), col=c('black', colors(1:3)), pch=rep('-',3), lwd=5)
  }
}
difference_plot(data_full, gt)
```

```{r}
difference_plot(round(data_full,1), round(gt[1:6],1))
```

```{r}
difference_plot2 <- function(df, gt) {
  df <- df[df$id %in% gt$id,]
  gt <- gt[gt$id %in% df$id,]
  for (trait_idx in 1:5) {
    pi_idx <- trait_idx + 1
    yark_idx <- trait_idx + 6
    golb_idx <- trait_idx + 11
    
    ordered_df <- normalize_data(df[order(df[,trait_idx+1]),])
    
    plot(1:nrow(ordered_df), ordered_df[,pi_idx], type='n',
         main=paste0('Ordered scores [',traits[[trait_idx]],']'),
         xlab='People',
         ylab='Absolute difference')
    lines(1:nrow(ordered_df), ordered_df[,pi_idx], col=alphcolor('c1',0.8))
    lines(1:nrow(ordered_df), ordered_df[,yark_idx], col=alphcolor('c2',0.8))
    lines(1:nrow(ordered_df), ordered_df[,golb_idx], col=alphcolor('c3',0.8))
    legend(x="topleft", y=0.92, c('pi','yarkoni','golbeck'), col=c(color$c1, color$c2, color$c3), pch=rep('-',3), lwd=5)
    break
  }
}
difference_plot2(data_full, gt)
```

```{r}
data_freqfilt <- read_single_db('selected_dev_parsed_frequency', transformations=transformations)
```

```{r}
# Check the RMSE on each personality trait.
measure_plot(dfs=list(data_full,data_freqfilt), dfnames=c('normal','freq'), gt=gt, func=RMSE)
measure_plot(dfs=list(data_full,data_freqfilt), dfnames=c('normal','freq'), gt=gt, func=MAE)
```

