---
title: "Research Question 4 - merged values"
author: "Frenk C.J. van Mil"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
---

```{r, result='hide', echo=FALSE, include=FALSE}
source('statistics.R')
source('rq4.R')

dbname <- 'selected_dev_parsed'
```

### Read the data
```{r, results='hide', echo=FALSE, include=FALSE}
transformations <- list(
  c(13, log10_transform)
)
# Read the database values
mysql <- get_connection()
data <- read_single_db(dbname, transformations=transformations)
data <- normalize_data(data)
data[,-1] <- round(data[,-1], 2)
dbDisconnect(mysql)

# Read the participants.
participants <- readcsv('../data/final_participants.csv')

detach('package:dplyr', unload=TRUE)
library(dplyr)
EPI <- participants %>% select(id, EPI) %>% filter(EPI != 'Unknown')
EPI <- merge(EPI, data, by="id")
EPI$EPI[EPI$EPI == "Very low"] <- "Low"
EPI$EPI[EPI$EPI == "Very high"] <- "High"
epi_order <- c("Low", "Moderate", "High")
EPI$EPI <- factor(EPI$EPI, levels=epi_order)
EPI <- EPI[order(EPI$EPI),]
EPI
```

### Box plots
```{r warning=FALSE}
# Suppressed warning for removed NA values.
boxplots_rq4()
```

### Density plots
```{r}
density_rq4()
```

```{r}
dfs <- get_seperate_lists(EPI, 2, epi_order)
```

### Normality with QQ-Plots
```{r}
draw_qqplots_rq4(dfs, dfnames=epi_order)
```


```{r}
repeated_shap_rq4()
```

We now check for normality with Shapiro-Wilk. The values reported above are for the Very low, Low, Moderate, High, and Very high EPI. '2 FALSE : 692' means that for column 2 (pi_openness) 692 FALSE was given for p<0.05 (and 308 times TRUE). In this case we would conclude normality, as there is no significance for non-normality. Columns start from 2 to 16 with OCEAN ordered Big Five traits in the order of PI, Yarkoni, and Golbeck.

### Show the variances of the different methods for each EPI level
```{r}
variances_rq4()
```

In the figure, we can see that PI has more variance than Yarkoni, and Yarkoni has more variance than Golbeck. We can also observe a slight decrease in variance from 'Very low' to 'Very high' EPI.

## Check for a difference in means with Wilcoxon signed-rank test.
```{r}
compare(wilc, dfs, dfnames=epi_order, paired=FALSE, p=0.05)
```

## Check for a difference in means with t-test.
```{r}
compare(ttest, dfs, dfnames=epi_order, paired=FALSE, p=0.05)
```

## Check for effect size in means with Cohen's d.
```{r}
compare(cohensd, dfs, dfnames=epi_order, paired=FALSE)
```


## Check for a difference in variance with Fisher F-test.
```{r}
compare(fisherf, dfs, dfnames=epi_order, p=0.05)
```


